CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-17 paper.Rmd
Minor changes to paper.

```{r}
# (5) Review results using the saved pins
# Establish the pinboard
pinboard <- file.path("ExampleFolder", "OutputData", "PipelineReleases") |> 
  pins::board_folder(versioned = TRUE)
# Look at the psut data frame
# created by the PFUDatabase pipeline
psut <- pinboard |>
  pins::pin_read("psut", version = "20230811T122618Z-3b7b3")
head(psut)
# Each column of the psut data frame contains matrices.
# The data are stored as sparse matrices,
# but easier to see as regular matrices.
psut$R[[1]] |> 
  as.matrix()

>>>>

```{r}
# (5) Review results using the saved pins
# Establish the pinboard
pinboard <- file.path("ExampleFolder", "OutputData", "PipelineReleases") |> 
  pins::board_folder(versioned = TRUE)
# Look at the psut data frame
# created by the PFUDatabase pipeline
psut <- pinboard |>
  pins::pin_read("psut", version = "20230811T122618Z-3b7b3")
head(psut)
# Each column of the psut data frame contains sparse matrices.
colnames(psut$R[[1]])
psut$R[[1]]
